### 2017-08-01 Tran Nott Kohn/importanceSampling.tex
misc

\section{Updating the VB Approximation}

@@

@@

>>>>

\section{Updating with the Bootstrap Particle Filter}

@@

\section{Using the Data-Driven Particle Filter}

The measurement equation for the SVM is
\begin{equation}
\label{measure}
y_t = h(x_t, \eta_t) =\exp\{0.5 x_t\} \eta_t,
\end{equation}
leading to particles $x_t$ being generated according to
\begin{equation}
\label{measureInv}
x_t = 2 \log(y_t / \eta_t).
\end{equation}
Weights are then calculated according to
\begin{align}
\label{DPFweight}
w_t^{(j)} &= \pi_t^{(j)} \left| \frac{\delta h(x_t^{(j)}, \eta_t^{(j)})}{\delta x_t^{(j)}} \right|^{-1}_{\eta_t = \eta_t^{(j)}, x_t = x_t^{(j)}} p\left(x_t^{(j)} | x_{t-1}^{(j)}\right) \nonumber \\
&= \pi_t^{(j)} \left| 0.5 \exp\{0.5 x_t^{(j)}\} \eta_t^{(j)} \right|^{-1} p \left(x_t^{(j)} | x_{t-1}^{(j)} \right)
\end{align}

@@

\section{General Loss Distributions}

To implement Bissiri et al. 2016 we need to write a loss function of the past data in terms of the parameters of interest, $x_{T+1}$ and  $\theta$.

Consider
\begin{equation}
\label{loss}
l(y | \theta, x_{T+1}) = -\sum_{t=1}^T \log(y_t | x_t),
\end{equation}
where
\begin{equation}
\label{lossyt}
\log(y_t | x_t) = c + 0.5x_t + \frac{y_t^2}{2 \exp(x_t)}.
\end{equation}
The recursion
\begin{equation}
\label{xRecursion}
x_t = \mu + \frac{x_{t+1} - \mu - \epsilon_{t+1}}{\phi}
\end{equation}
allows each $x_t$ to be recovered given a sequence of $iid$ standard normal random variables $\epsilon_t, t = 1, \dots, T+1$.
